A performance assessment of evolutionary algorithms in a volunteer computing system

### 2016-03-12 PPSN2016/paper.Rnw
Solving data problems
One of the files was duplicated, it's been rearranged now. Table also fixed.

these.experiments <- c("nooverlap-1","nooverlap-newgraph", "nooverlap-newgraph-2","nooverlap-newgraph-3","nooverlap-newgraph-reboot","nooverlap-newgraph-reboot-cachecrash")

@@

\begin{table}[htb]
\caption{Experiment table, with summary of results. \label{tab:runs}}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
Experiment & Time (ms) & \multicolumn{2}{|c|}{IPs} & \multicolumn{2}{|c|}{PUTs} & \#Runs\\
           &           & Total & Contributing & Total & Contributing & \\
\hline
base & 120056.0 & 10 & 4 & 256.0 & 21.0 & 81\\
\hline
graph1 & 152619.5 & 9 & 4 & 212.5 & 26.5 & 36\\
graph2 & 152619.5 & 9 & 4 & 212.5 & 26.5 & 36\\
graph3 & 1173561.5 & 6 & 4 & 761.5 & 22.0 & 36\\
\hline
reboot & 513354.5 & 9 & 6 & 545.5 & 62.5 & 40\\
\hline
cachereboot & 392917.0 & 12 & 12 & 576.0 & 79.0 & 55\\
\hline
\end{tabular}
%% Initially generated with this code, 
%% <<experiments, cache=FALSE,echo=FALSE>>=
%% experiment.aggregates$Experiment <- c("base","graph1","graph2","graph3","reboot","cachereboot")
%% kable(experiment.aggregates)
%% @ %def

>>>>

these.experiments <- c("nooverlap-1","nooverlap-newgraph-1", "nooverlap-newgraph-2","nooverlap-newgraph-reboot","nooverlap-newgraph-reboot-cachecrash")

@@

\begin{table}[htb]
\caption{Experiment table, with summary of results. \label{tab:runs}}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|}
\hline
Experiment & Time (ms) & \multicolumn{2}{|c|}{IPs} & \multicolumn{2}{|c|}{PUTs} & \#Runs\\
           &           & Total & Contributing & Total & Contributing & \\
\hline
base & 120056.0 & 10 & 4 & 256.0 & 21.0 & 81\\
\hline
graph1 & 152619.5 & 9 & 4 & 212.5 & 26.5 & 36\\
graph2 & 1173561.5 & 6 & 4 & 761.5 & 22.0 & 36\\
\hline
reboot & 513354.5 & 9 & 6 & 545.5 & 62.5 & 40\\
\hline
cachereboot & 392917.0 & 12 & 12 & 576.0 & 79.0 & 55\\
\hline
\end{tabular}
%% Initially generated with this code, 
%% <<experiments, cache=FALSE,echo=FALSE>>=
%% experiment.aggregates$Experiment <- c("base","graph1","graph2","graph3","reboot","cachereboot")
%% kable(experiment.aggregates)
%% @ %def
